### 2015-03-11 manuscript/plos_template.tex
various change

The Figure \ref{nature2013_sig_summary},  \ref{nature2013_sig_member} shows the summary of the obtained mutation signatures.
In total, 27 mutation signatures were extracted.
The signature 6 (C $>$ T at NpCpG sites) was observed in 25 out of 30 cancer type, and related to deamination of 5-methyl-cytosine.
The signature 13 (T $>$ [AGT] at TpCpN sites) was observed in 11 cancer types, and related to the activity of APOBEC family.
The signature 7 and the signature 1 (C $>$ T at TpCpG and C $>$ A at TpCpT, respectively) were observed in colorectal and uterine cancers,
and associated with deregulated activity of the error-prone polymerase Pol $\epsilon$.
Interestingly, for representing the signature for the Pol $\epsilon$ dysfunction, which was represented by one signature in the previous study,
the proposed method utilized two mutation signatures for compensating simplified representation powers.
The signature 8 (C $>$ T at NpCp[CT]) were observed in melanomas and glioblastomas, 
and seems to be associated with temozolomide, an anticancer drug.
The signature 9 (C $>$T at [CT]pCpC) were observed in head and neck cancers and melanomas, and probably related to ultraviolet light.
The signature 10 (C $>$ T at GpCp[CG]) were observed in small-cell lung cancers and stomach cancers,
and seems to be the same with the ``signature 15'' in the previous study, whose function is still not clear.

In addition to the above signatues, a number of prominent mutation signatures observed in one cancer type 
had common characteristics with those observed in the previous study:
the signature 20 (T $>$ [CG] at CpTpT) observed in oesophagus cancers, 
the signature 2 (C $>$ A at [CT]pCpT) observed in low grade gliomas,
the signature 5 (C $>$ A at NpCp[AT]) observed in neuroblastomas,
the signature 12 (C $>$ T at [CG]pCp[CT]) observed in pilocytic astrocytomas, 
and the signature 18 (T $>$ C at GpTpN) in stomach cancers.

@@

@@

\subfigure[Signature intensities at two 5' to the mutated site]{%
  \includegraphics[width=8cm,height=5cm]{APOBEC_two5prime.eps}
  \label{APOBEC_twofive}}

>>>>

The Figure \ref{nature2013_sig_summary},  \ref{nature2013_sig_member} shows the summary of the obtained mutation signatures.
In total, 27 mutation signatures were extracted.
By comparing the composition of nucleotides and memberships of signatures with the result of the previous study,
we could associate many of the detected signatures with known mutational processes.

The signature 13 (T $>$ [AGT] at TpCpN sites) was observed in 12 cancer types, and related to the activity of APOBEC family.
The composition of nucleotides in estimated signatures in 12 different cancer types are highly consistent (Figure \ref{APOBEC_sig_list}) except for the on in B-cell lymphoma,
and almost of of them showed slightly higher abundance of A and T bases and depletion of G base at $-2$ positions (Figure \ref{APOBEC_twofive}).
This fact backs up the results obtained from UCUT data in the previous subsection and the previous study \cite{pmid23318258},
and implies the robustness of the proposed approach.
In terms of transcribed strand-specificity, the tendency is not consistent, implying that there is no significant strand-specificity in APOBEC signatures.

The signature 1 and 8 (C $>$ A at TpCpT and C $>$ T at TpCpG, respectively) were observed in colorectal and uterine cancers,
are probably associated with deregulated activity of the error-prone polymerase Pol $\epsilon$.
The proposed method used two signatures for representing the signature for the Pol $\epsilon$ dysfunction, 
while was represented by one signature in the previous study.
Interestingly, signature 1 showed transcription biases whereas signature 8 did not.
This phenomena are consistent for both colorectal and uterus cancers (Figures \ref{POLE1_sig_list} and \ref{POLE2_sig_list}).
C $>$A at TpCpT mutations were shown to be enriched in leading strands of replication forks.
whereas, there is no mention about the replication strand-specificity of C $>$ T at TpCpG mutations \cite{pmid25228659}.
Although replication strand biases is different from the transcription strand biases, these two biases may have strong corelation,
considering the fact that replication origins prefer transcription start sites \cite{pmid23187890}.
Therefore, the transcription strand bias observed in the signature 1 may actually come from replication strand biases.

Furthermore, both the signature 1 and 8 signatures showed strong abundance of T base at $-2$ positions,
and abundance of T bases at two bases 5' and 3' to the mutated site, respectively (Figures \ref{POLE1_sig_list} and \ref{POLE2_sig_list}).
In fact, nonsense mutations in TP53 at R231X, which are shown to be enriched in cancers having Pol $\epsilon$,
and abundance of T bases at two bases 5' and 3' to the mutated site, respectively (Figures \ref{POLE1_sig_list} and \ref{POLE2_sig_list}).
In the previous study of Pol $\epsilon$, a nonsense mutation in TP53 at R23X were shown to be enriched in cancers with Pol $\epsilon$ defects.
In fact, this mutation is C $>$ T at TpTpCpGpA, the most likely patten with the signature 8.
This implies that observing $\pm 2$ bases may be helpful for identifying the cause of mutations with higher resolution.

The signature 18 (T $>$ C at ApTp[AG]), observed in liver cancer, shows very strong strains specificity,
were shown to be more common in Asian cases than in other ancestries \cite{pmid25362482}, though the source of this signature is still not clear.

The signature 3 and 5 (C $>$ A at NpCpN), which were observed in head-and-neck cancers, three types of lung cancers,
are probably associated with tobacco smoking.
Furthermore, the fact that the estimated signature for each cancer shows higher prevalence on coding strands is consistent with the previous study.

The signature 7 (C $>$ T at NpCpG sites) was observed in 25 out of 30 cancer type, and related to deamination of 5-methyl-cytosine.
The signature 9 (C $>$ T at NpCp[CT]) were observed in melanomas and glioblastomas, 
and seems to be associated with a chemotherapy drug, temozolomide.

The signature 9 (C $>$T at [CT]pCpC) were observed in head and neck cancers and melanomas, and probably related to ultraviolet light.
The signature 10 (C $>$ T at GpCp[CG]) were observed in small-cell lung cancers and stomach cancers,
and seems to be the same with the ``signature 15'' in the previous study, whose function is still not clear.

The signature 2 (C $>$ A at [CT]pCpT), observed in low grade gliomas, can be related to the one detected in the same cancer type in the previous study, but slightly different. 
This seems to be because the corresponding signature in the previous study shows very complex pattern (C $>$ A at NpCpT or C $>$ T at GpTpN).
Actually, the mutation related to this signature is mostly coming from one cancer with a very high mutation rate.
When we re-analyze the data removing this sample, the signature 2 disappeared.
We suspect that the low-grade-glioma specific signature detected in the previous study may be aggregation of multiple signatures,
but cannot be decomposed due to the lack of samples having these signatures.
Therefore, we need to be more careful for the signature 2 and the corresponding signature in the previous study.

The signature 3 (C $>$ A at CpCpG), observed in several cancers,
Actually, this signature correspond to the one that could not be validated in the previous study,
and the pattern

In addition to the above signatures, a number of prominent mutation signatures observed in one cancer type 
had common characteristics with those observed in the previous study:
the signature 21 (T $>$ [CG] at CpTpT) observed in oesophagus cancers, 
the signature 2 (C $>$ A at [CT]pCpT) observed in low grade gliomas,
the signature 6 (C $>$ A at NpCp[AT]) observed in neuroblastomas,
the signature 12 (C $>$ T at [CG]pCp[CT]) observed in pilocytic astrocytomas, 
and the signature 19 (T $>$ C at GpTpN) in stomach cancers.

Although, our method detected most of the

@@

\subfigure[Smoking signature  in each cancer type]{%
  \includegraphics[width=15cm,height=2.5cm]{signatureList_LUNG.eps}
  \label{LUNG_sig_list}}

@@

% \subfigure[Signature intensities at two 5' to the mutated site]{%
% \includegraphics[width=8cm,height=5cm]{APOBEC_two5prime.eps}
 % \label{APOBEC_twofive}}
